---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`cvtmleAUC`

[![Travis-CI Build Status](https://travis-ci.org/benkeser/cvtmleAUC.svg?branch=master)](https://travis-ci.org/benkeser/cvtmleAUC)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/status/github/benkeser/cvtmleAUC?branch=master&svg=true)](https://ci.appveyor.com/project/benkeser/cvtmleAUC)
[![Coverage Status](https://img.shields.io/codecov/c/github/benkeser/cvtmleAUC/master.svg)](https://codecov.io/github/benkeser/cvtmleAUC?branch=master)
<!-- [![CRAN](http://www.r-pkg.org/badges/version/cvtmleAUC)](http://www.r-pkg.org/pkg/cvtmleAUC) -->
<!-- [![CRAN downloads](https://cranlogs.r-pkg.org/badges/cvtmleAUC)](https://CRAN.R-project.org/package=cvtmleAUC) -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![MIT license](http://img.shields.io/badge/license-MIT-brightgreen.svg)](http://opensource.org/licenses/MIT)
<!-- [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.835868.svg)](https://doi.org/10.5281/zenodo.835868) -->

> Cross-validated targeted minimum loss-based estimates of cross-validated area under the receiver operating characteristic curve

__Authors:__ [David Benkeser](https://www.benkeserstatistics.com/) 

---

## Description

`cvtmleauc` is an R package for computing cross-validated targeted minimum loss-based estimates of cross-validated area under the receiver operating characteristic curve (cvAUC). This package is under active development. 

---

## Installation

<!-- For standard use, we recommend installing the package from
[CRAN](https://cran.r-project.org/) via

```{r cran-installation, eval = FALSE}
install.packages("cvtmleAUC")
``` -->

You can install the current release of `cvtmleAUC` from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/) with:

```{r gh-installation, eval = FALSE}
devtools::install_github("benkeser/cvtmleAUC")
```

<!--
To contribute, install the _development version_ from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/):

```{r gh-develop-installation, eval = FALSE}
devtools::install_github("benkeser/cvtmleAUC", ref = "develop")
```
-->

---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/benkeser/cvtmleAUC/issues).

---
<!-- 
## Example

This minimal example shows how to use `cvtmleAUC` to obtain cumulative incidence
estimates with a very simple, simulated data set.

```{r example, fig.align='center'}
# simulate data
set.seed(341796)
n <- 100
t_0 <- 10
W <- data.frame(W1 = runif(n), W2 = rbinom(n, 1, 0.5))
A <- rbinom(n, 1, 0.5)
T <- rgeom(n,plogis(-4 + W$W1 * W$W2 - A)) + 1
C <- rgeom(n, plogis(-6 + W$W1)) + 1
ftime <- pmin(T, C)
ftype <- as.numeric(ftime == T)

# load the package
library(cvtmleAUC)

# apply cvtmleAUC for estimation
fit <- cvtmleAUC(ftime = ftime, ftype = ftype,
                trt = A, adjustVars = W,
                glm.trt = "1",
                glm.ftime = "I(W1*W2) + trt + t",
                glm.ctime = "W1 + t", method = "hazard",
                t0 = t_0)

# extract cumulative incidence at each timepoint
tpfit <- timepoints(fit, times = seq_len(t_0))

# examine output object produced by the timepoints function
tpfit

# examine plot of cumulative incidences
plot(tpfit)
```

---

## Contributions

Contributions are very welcome. Interested contributors can consult our [`contribution guidelines`](https://github.com/benkeser/cvtmleAUC/blob/master/CONTRIBUTING.md) prior to submitting a pull request.

---

## Citation

After using the `cvtmleAUC` R package, please cite both of the following:

        @misc{benkeser2017cvtmleAUC,
          author = {Benkeser, David C and Hejazi, Nima S},
          title = {{cvtmleAUC}: Targeted Minimum Loss-Based Estimation for
                   Survival Analysis in {R}},
          year  = {2017},
          howpublished = {\url{https://github.com/benkeser/cvtmleAUC}},
          url = {http://dx.doi.org/10.5281/zenodo.835868},
          doi = {10.5281/zenodo.835868}
        }

        @article{benkeser2017improved,
          author = {Benkeser, David C and Carone, Marco and Gilbert, Peter B},
          title = {Improved estimation of the cumulative incidence of rare
                   outcomes},
          journal = {Statistics in Medicine},
          publisher = {Wiley-Blackwell},
          year  = {2017},
          doi = {10.1002/sim.7337}
        }

--- -->

## License

&copy; 2016-2017 [David C. Benkeser](http://www.benkeserstatistics.com)

The contents of this repository are distributed under the MIT license. See
below for details:
```
The MIT License (MIT)

Copyright (c) 2018 David C. Benkeser

Permission is hereby granted, free of charge, to any person obtaining a copy
of this software and associated documentation files (the "Software"), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all
copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
SOFTWARE.
```
